A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-08-10 refl_maths/paper.tex
A commit to the refl_maths directory
a change to tex
cleanup plots.py

The collected data (once normalised) is described in terms of reflected intensity, $R(q)$, which depends on the wavevector, $q$, and is measured as,
%
%ARJN, how about how to calculate the wavevector from a vector sum? i.e. something similar to fig 2, augmented with ki, kf.
%ARM Do you mean something like the $|k_i|\sin{\theta} = |k_f|\sin{\theta} = \frac{2\pi}\sin{\theta} = \frac{|\mathbf{q}|}{2} = \frac{q}{2}$ as a why of explaining what the $q$-vector is? I agree that it is necessary to explain what $q$ is but how about we just give the $q = \frac{4\pi\sin{\theta}}{\lambda} and explain that a full derivation can be found elsewhere \cite{sivia_elementary_2011}
\begin{equation}
    R(q) = \frac{\text{specular reflected intensity at $q$}}{\text{incident radiation intensity}},
    \label{equ:refl}
\end{equation}
%
where the denominator in Equation~\ref{equ:refl} is the total flux of X-rays or neutrons on the sample.
It is this $R(q)$ that we want to calculate from our structural model and then compare with our data.

@@

\section*{Author Contributions}
ARM wrote the first draft of this text, and ARJN and TS offered input on additional content to cover and clarifications to include.

proposed, implemented, and applied the Bayesian model comparison framework, with input from T.A., J.F.K.C. and T.S.; J.F.K.C. and T.S. sourced funding; A.R.M. wrote the manuscript, with input from all authors.

>>>>

The collected data (once normalised) is described in terms of reflected intensity, $R(q)$, which depends on the wavevector, $q$, and is measured as,
%
\begin{equation}
    R(q) = \frac{\text{specular reflected intensity at $q$}}{\text{incident radiation intensity}},
    \label{equ:refl}
\end{equation}
%
where the denominator in Equation~\ref{equ:refl} is the total flux of X-rays or neutrons on the sample.
The wavevector, $q$, depends on the scattering angle, $\theta$, and wavelength, $\lambda$, of the incident radiation, 
%
\begin{equation}
    q = \frac{4\pi\sin{\theta}}{\lambda}.
\end{equation}
%
The full derivation of this elastic scattering wavevector can be found in the work of Sivia \cite{sivia_elementary_2011}. 
It is this $R(q)$ that we want to calculate from our structural model and then compare with our data.

@@

\section*{Author Contributions}
ARM wrote the first draft of this text, with ARJN, TS, JMCL, TA, JFKC offering additional content and editing.
 JFKC and TS sourced funding.
